Analysis : exp220 - 228 (Nov 2018, for J Neurophys draft 2018)

### 2020-04-24 resistingrhythm/analysis/paper_figures_v4.Rmd
Renamed 'rate' to 'modulation' in all Figures

## FI curve
```{r, message=FALSE}
results_fi <- read_csv("../ipynb/FI_curves.csv")
```
# Figure: Theta results
```{r fig.height=2.25, fig.width=6}
# Kappa no H, E
bind_rows(results220, results222) %>%
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>% 
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, color=synapse)) +
    geom_line(size=0.8) +
    geom_point(size=1.5) +
    geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse)) +
    scale_color_manual(values=c("black", "grey")) +
    lims(y=c(0.0, 0.2)) +
    labs(title="b.", y="Kappa", x="Osc. rate") +
    theme_classic2() +
    theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
          legend.position="none") -> p1

# Kappa with H, E
bind_rows(results221, results223) %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, color=synapse)) +
    geom_line(size=0.8) +
    geom_point(size=1.5) +
    geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
                  width=.15, size=0.2) +
    scale_color_manual(values=c("black", "grey")) +
    lims(y=c(0.0, 0.2)) +
    labs(title="d.", y="Kappa", x="Osc. rate") +
    theme_classic2() +
    theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
          legend.position="none") -> p2

# Rate no H, E
bind_rows(results220, results222) %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>% 
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M,color=synapse)) +
  geom_line(size=0.8) +
    geom_point(size=1.5) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
                width=.15, size=0.2) +
  scale_color_manual(values=c("black", "grey")) +
  labs(title="a.", y="Pop. rate", x="Osc. rate") +
  lims(y=c(0.0, 180.0)) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme_classic2() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
        legend.position="none") -> p3

# -
# Rate, with H, E
bind_rows(results221, results223) %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, color=synapse)) +
  geom_line(size=0.8) +
    geom_point(size=1.5) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
                width=.15, size=0.2) +
  scale_color_manual(values=c("black", "grey"), name="Tonic") +
  labs(title="c.", y="Pop. rate", x="Osc. rate") +
  lims(y=c(0.0, 180.0)) +
  theme_classic2() +
  theme(
    legend.position = c(-.5, -0.2),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p4

# --------------------------------------------------------
bind_rows(results224, results227)  %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, color=synapse)) +
    geom_line(size=0.8) +
    geom_point(size=1.5) +
    geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
                width=.15, size=0.2) +
    scale_color_manual(values=c("darkgoldenrod3", "goldenrod1")) +
    lims(y=c(0.0, 0.2)) +
    labs(title="f.", y="Kappa", x="Osc. rate") +
    theme_classic2() +
    theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
          legend.position="none") -> p5

# -
bind_rows(results224, results227)  %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, color=synapse)) +
    geom_line(size=0.8) +
    geom_point(size=1.5) +
    geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
                width=.15, size=0.2) +
    scale_color_manual(values=c("darkgoldenrod3", "goldenrod1"), name="Burst") +
    labs(title="e.", y="Pop. rate", x="Osc. rate") +
    lims(y=c(0.0, 180.0)) +
    theme_classic2() +
  theme(
    legend.position = c(1.5, -1.25),
    legend.title = element_text(colour = 'darkgoldenrod3'),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p6

@@

```{r}
print(wilcox.test(x=tmp3$rate_k, y=tmp4$rate_k))
```
# Figure: FI 
```{r, fig.height=0.9, fig.width=1.9}
win <- 50e-3
N <- 100
us <- 1e6
results_fi %>% 
ggplot() +
  geom_line(aes(x=impulse*us, y=rate_ref/win/N, color="No homeostatis"), size=0.8) +
  geom_line(aes(x=impulse*us, y=rate_h/win/N, color="Homeostatis"), size=0.8) +
  labs(tag="a.", y="Avg. rate", x=TeX("Impulse ($\\mu$siemens)")) +
  lims(x=c(0, 10)) +
  scale_colour_manual(values=c("black", "grey")) +
  theme_classic() +
  theme(
    legend.title = element_blank(),
    plot.tag = element_text(size=18, face="bold"),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm")
  ) -> p1
print(p1)

png(file="fig3.png", bg="white", width=3.8, height=1.8, unit="in", res=300)
print(p1)
dev.off()
```

# Figure: Gamma (AMPA)
```{r, fig.height=2.1, fig.width=2.8}
freq_labels <- as_labeller(c('60' = "60 Hz", '90' = "90 Hz"))
gamma_results %>% 
  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
  filter(homeo == "Homeostasis") %>% 
  group_by(freq, osc_rate, kind) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=kind)) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=kind), size=.4) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  theme_classic() +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  labs(y="Pop. rate", x="Osc. rate", tag="a.") +
  lims(y=c(0, 100)) +
  theme(legend.position = c(1.17, -0.5),
        plot.tag = element_text(size=16, face="bold"),
        legend.background = element_rect(colour ="black"),
        panel.spacing = unit(1, "lines"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank()) +
  facet_grid(.~freq, scales = "free", labeller=freq_labels) -> p1

gamma_results %>% 
  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
  filter(homeo == "Homeostasis") %>% 
  group_by(freq, osc_rate, kind) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=kind)) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=kind), size=.4) +
  theme_classic() +
  facet_grid(.~freq, scales = "free", labeller = freq_labels) +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  lims(y=c(0.0, .12)) +
  theme(legend.position = "none",
        plot.tag = element_text(size=16, face="bold"),
        panel.spacing = unit(1, "lines"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank()) +
  labs(y="Kappa", x="Osc. rate", tag="b.") -> p2

@@

png(file="fig4.png", bg="white", width=5.6, height=4.2, unit="in", res=300)
grid.arrange(p1, p2, pn,layout_matrix=layout_matrix)
dev.off()
```

@@

tmp1 %>% 
  ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, 
                                           levels = c(0.0026, 0.0028, 0.003, 0.0032, 0.0034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_linerange(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="b.", y="Kappa", x="Osc. rate") +
  scale_color_manual(
    values=c("plum1", "plum2", "black", "plum3", "plum4"), 
    guide=FALSE) +
  theme_classic2() +
  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p1

@@

tmp2 %>% 
ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, 
                                         levels = c(0.0026, 0.0028, 0.003, 0.0032, 0.0034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_linerange(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="a.", y="Pop. rate", x="Osc. rate") +
  scale_color_manual(
    values=c("plum1", "plum2", "black", "plum3", "plum4"), 
    name="Target [Ca]\n(mmolar)") +
  theme_classic2() +
  theme(
    plot.title = element_text(hjust = -.5, size=18, face="bold"),
    legend.position = c(1.35, -0.5),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm")) -> p2

@@

# -----------------------------------------------------------------------------------
# Freq Theta drift
results_control_drift %>% 
  filter(homeo=="Homeostasis") %>% 
  group_by(osc_rate, freq) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=as.factor(freq))) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=as.factor(freq)), size=.4) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  theme_classic() +
  labs(tag="d.", y="Pop. rate", x="Osc. rate") +
  lims(y=c(0.0, 100.0)) +
  theme(
    legend.position = c(1.35, -0.4),
    legend.key.size = unit(.4, "cm"),
    legend.background = element_rect(colour ="black"),
    plot.tag = element_text(size=18, face="bold")) +
  scale_color_manual(
    values=c("darkslategray3", "darkslategray4", "black", "darkolivegreen4", "darkolivegreen3"), 
    name="Freq. (Hz)") -> p10

results_control_drift %>% 
  filter(homeo=="Homeostasis") %>% 
  group_by(osc_rate, freq) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=as.factor(freq))) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=as.factor(freq)), size=.4) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  theme_classic() +
  labs(tag="e.", y="Kappa", x="Osc. rate") +
  lims(y=c(0.0, 0.2)) +
  theme(legend.position = "none",
        plot.tag = element_text(size=18, face="bold")) +
  scale_color_manual(
    values=c("darkslategray3", "darkslategray4", "black", "darkolivegreen4", "darkolivegreen3"), 
    name="Freq. (Hz)") -> p11

# -----------------------------------------------------------------------------------
results_control_leak %>% 
  filter(homeo=="Homeostasis") %>% 
  group_by(osc_rate, homeo, g_L) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=g_L)) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=g_L), size=.4) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  theme_classic() +
  theme(
    legend.position = c(1.35, -0.4),
    legend.key.size = unit(.4, "cm"),
    legend.background = element_rect(colour ="black"),
    plot.tag = element_text(size=18, face="bold")) +
  labs(tag="f.", y="Pop. rate", x="Osc. rate") +
  scale_color_manual(
    values=c("darkorange3", "darkorange4", "black", "gold4", "gold3"), 
    name="g_L (siemens)") -> p14

results_control_leak %>% 
  filter(homeo=="Homeostasis") %>% 
  group_by(osc_rate, homeo, g_L) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=g_L)) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=g_L), size=.4) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  theme_classic() +
  theme(legend.position = "none",
        plot.tag = element_text(size=18, face="bold")) +
  labs(tag="g.", y="Kappa", x="Osc. rate") +
  theme(plot.tag = element_text(size=16, face="bold")) + 
  scale_color_manual(
    values=c("darkorange3", "darkorange4", "black", "gold4", "gold3"), 
    name="g_L (siemens)") -> p15

>>>>

## FI curve
```{r, message=FALSE}
results_fi <- read_csv("../ipynb/FI_curves.csv")
```
# Figure: Theta results
```{r fig.height=2.25, fig.width=6}
# Kappa no H, E
bind_rows(results220, results222) %>%
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>% 
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, color=synapse)) +
    geom_line(size=0.8) +
    geom_point(size=1.5) +
    geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse)) +
    scale_color_manual(values=c("black", "grey")) +
    lims(y=c(0.0, 0.2)) +
    labs(title="b.", y="Kappa", x="Osc. modulation") +
    theme_classic2() +
    theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
          legend.position="none") -> p1

# Kappa with H, E
bind_rows(results221, results223) %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, color=synapse)) +
    geom_line(size=0.8) +
    geom_point(size=1.5) +
    geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
                  width=.15, size=0.2) +
    scale_color_manual(values=c("black", "grey")) +
    lims(y=c(0.0, 0.2)) +
    labs(title="d.", y="Kappa", x="Osc. modulation") +
    theme_classic2() +
    theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
          legend.position="none") -> p2

# Rate no H, E
bind_rows(results220, results222) %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>% 
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M,color=synapse)) +
  geom_line(size=0.8) +
    geom_point(size=1.5) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
                width=.15, size=0.2) +
  scale_color_manual(values=c("black", "grey")) +
  labs(title="a.", y="Pop. rate", x="Osc. modulation") +
  lims(y=c(0.0, 180.0)) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme_classic2() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
        legend.position="none") -> p3

# -
# Rate, with H, E
bind_rows(results221, results223) %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, color=synapse)) +
  geom_line(size=0.8) +
    geom_point(size=1.5) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
                width=.15, size=0.2) +
  scale_color_manual(values=c("black", "grey"), name="Tonic") +
  labs(title="c.", y="Pop. rate", x="Osc. modulation") +
  lims(y=c(0.0, 180.0)) +
  theme_classic2() +
  theme(
    legend.position = c(-.5, -0.2),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p4

# --------------------------------------------------------
bind_rows(results224, results227)  %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, color=synapse)) +
    geom_line(size=0.8) +
    geom_point(size=1.5) +
    geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
                width=.15, size=0.2) +
    scale_color_manual(values=c("darkgoldenrod3", "goldenrod1")) +
    lims(y=c(0.0, 0.2)) +
    labs(title="f.", y="Kappa", x="Osc. modulation") +
    theme_classic2() +
    theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
          legend.position="none") -> p5

# -
bind_rows(results224, results227)  %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, color=synapse)) +
    geom_line(size=0.8) +
    geom_point(size=1.5) +
    geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
                width=.15, size=0.2) +
    scale_color_manual(values=c("darkgoldenrod3", "goldenrod1"), name="Burst") +
    labs(title="e.", y="Pop. rate", x="Osc. modulation") +
    lims(y=c(0.0, 180.0)) +
    theme_classic2() +
  theme(
    legend.position = c(1.5, -1.25),
    legend.title = element_text(colour = 'darkgoldenrod3'),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p6

@@

```{r}
print(wilcox.test(x=tmp3$rate_k, y=tmp4$rate_k))
```
# Figure: Gamma (AMPA)
```{r, fig.height=2.1, fig.width=2.8}
freq_labels <- as_labeller(c('60' = "Gamma, 60 Hz", '90' = "Gamma, 90 Hz"))
gamma_results %>% 
  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
  filter(homeo == "Homeostasis") %>% 
  group_by(freq, osc_rate, kind) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=kind)) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=kind), size=.4) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  theme_classic() +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  labs(y="Pop. rate", x="Osc. modulation", tag="a.") +
  lims(y=c(0, 100)) +
  theme(legend.position = c(1.17, -0.5),
        plot.tag = element_text(size=16, face="bold"),
        legend.background = element_rect(colour ="black"),
        panel.spacing = unit(1, "lines"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank()) +
  facet_grid(.~freq, scales = "free", labeller=freq_labels) -> p1

gamma_results %>% 
  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
  filter(homeo == "Homeostasis") %>% 
  group_by(freq, osc_rate, kind) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=kind)) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=kind), size=.4) +
  theme_classic() +
  facet_grid(.~freq, scales = "free", labeller = freq_labels) +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  lims(y=c(0.0, .12)) +
  theme(legend.position = "none",
        plot.tag = element_text(size=16, face="bold"),
        panel.spacing = unit(1, "lines"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank()) +
  labs(y="Kappa", x="Osc. modulation", tag="b.") -> p2

@@

png(file="fig3.png", bg="white", width=5.6, height=4.2, unit="in", res=300)
grid.arrange(p1, p2, pn,layout_matrix=layout_matrix)
dev.off()
```

# Figure: FI 
```{r, fig.height=0.9, fig.width=1.9}
win <- 50e-3
N <- 100
uamp <- 1e6
results_fi %>% 
ggplot() +
  geom_line(aes(x=impulse*uamp, y=rate_ref/win/N, color="No homeostatis"), size=0.8) +
  geom_line(aes(x=impulse*uamp, y=rate_h/win/N, color="Homeostatis"), size=0.8) +
  labs(tag="a.", y="Pop. rate", x=TeX("Impulse ($\\mu$amps)")) +
  lims(x=c(0, 10)) +
  scale_colour_manual(values=c("black", "grey")) +
  theme_classic() +
  theme(
    legend.title = element_blank(),
    plot.tag = element_text(size=18, face="bold"),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm")
  ) -> p1
print(p1)

png(file="fig4.png", bg="white", width=3.8, height=1.8, unit="in", res=300)
print(p1)
dev.off()
```

@@

tmp1 %>% 
  ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, 
                                           levels = c(0.0026, 0.0028, 0.003, 0.0032, 0.0034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_linerange(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="b.", y="Kappa", x="Osc. modulation") +
  scale_color_manual(
    values=c("plum1", "plum2", "black", "plum3", "plum4"), 
    guide=FALSE) +
  theme_classic2() +
  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p1

@@

tmp2 %>% 
ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, 
                                         levels = c(0.0026, 0.0028, 0.003, 0.0032, 0.0034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_linerange(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="a.", y="Pop. rate", x="Osc. modulation") +
  scale_color_manual(
    values=c("plum1", "plum2", "black", "plum3", "plum4"), 
    name="Target [Ca]\n(mmolar)") +
  theme_classic2() +
  theme(
    plot.title = element_text(hjust = -.5, size=18, face="bold"),
    legend.position = c(1.35, -0.5),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm")) -> p2

@@

# -----------------------------------------------------------------------------------
# Freq Theta drift
results_control_drift %>% 
  filter(homeo=="Homeostasis") %>% 
  group_by(osc_rate, freq) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=as.factor(freq))) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=as.factor(freq)), size=.4) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  theme_classic() +
  labs(tag="d.", y="Pop. rate", x="Osc. modulation") +
  lims(y=c(0.0, 100.0)) +
  theme(
    legend.position = c(1.35, -0.4),
    legend.key.size = unit(.4, "cm"),
    legend.background = element_rect(colour ="black"),
    plot.tag = element_text(size=18, face="bold")) +
  scale_color_manual(
    values=c("darkslategray3", "darkslategray4", "black", "darkolivegreen4", "darkolivegreen3"), 
    name="Freq. (Hz)") -> p10

results_control_drift %>% 
  filter(homeo=="Homeostasis") %>% 
  group_by(osc_rate, freq) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=as.factor(freq))) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=as.factor(freq)), size=.4) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  theme_classic() +
  labs(tag="e.", y="Kappa", x="Osc. modulation") +
  lims(y=c(0.0, 0.2)) +
  theme(legend.position = "none",
        plot.tag = element_text(size=18, face="bold")) +
  scale_color_manual(
    values=c("darkslategray3", "darkslategray4", "black", "darkolivegreen4", "darkolivegreen3"), 
    name="Freq. (Hz)") -> p11

# -----------------------------------------------------------------------------------
results_control_leak %>% 
  filter(homeo=="Homeostasis") %>% 
  group_by(osc_rate, homeo, g_L) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=g_L)) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=g_L), size=.4) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  theme_classic() +
  theme(
    legend.position = c(1.35, -0.4),
    legend.key.size = unit(.4, "cm"),
    legend.background = element_rect(colour ="black"),
    plot.tag = element_text(size=18, face="bold")) +
  labs(tag="f.", y="Pop. rate", x="Osc. modulation") +
  scale_color_manual(
    values=c("darkorange3", "darkorange4", "black", "gold4", "gold3"), 
    name="g_L (siemens)") -> p14

results_control_leak %>% 
  filter(homeo=="Homeostasis") %>% 
  group_by(osc_rate, homeo, g_L) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(aes(x=osc_rate, y=M, color=g_L)) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=g_L), size=.4) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  theme_classic() +
  theme(legend.position = "none",
        plot.tag = element_text(size=18, face="bold")) +
  labs(tag="g.", y="Kappa", x="Osc. modulation") +
  theme(plot.tag = element_text(size=16, face="bold")) + 
  scale_color_manual(
    values=c("darkorange3", "darkorange4", "black", "gold4", "gold3"), 
    name="g_L (siemens)") -> p15
